---
title: Easy Latex Titles and Labels for ggplot
author: 'Matthew Parker'
date: '2018-08-21'
slug: easy-latex-titles-and-labels-for-ggplot
categories:
  - ggplot
  - tikz
  - R
  - Tidyverse
tags:
  - ggplot
  - R
  - tikzDevice
  - tidyverse
  
header-includes:
  - \usepackage{tikz}
---

## Summary

Ever wanted to add $\LaTeX$ to your R plots? Well now you can, with **tikz**, and it will allow you to use $\LaTeX$ code within your plot titles, labels, and annotations. We're going to look at how to use $\LaTeX$ (text formating, formulas, fractions, greek letters, etc) with your **ggplot** data visualizations. We will be using the **tikzDevice** package for R (and to use your plots in $\LaTeX$, you will use the package **tikz**).

## Libraries

```{r hidden, echo=FALSE}
set.seed(11111)
```

Open up an R script! You will need to install these two libraries if you don't already have them:

```{r libs, message=FALSE, warning=FALSE}
library(ggplot2)
library(tikzDevice)
```

## Data

Unrelated to learning how to use **tikzDevice**, we need some data to play with. Here we will generate some data to plot:

```{r gen_data}
x     <- rnorm(n = 100, mean = 10, sd = 10)
alpha <- 2.0
beta  <- 1.5
gamm  <- 10
err   <- rnorm(n=100, mean=0, sd = 0.25)
f_x   <- alpha / (1 + exp(-1 * beta * (x - gamm))) + err

dat   <- data.frame(x=x, y=f_x)
```

Before we start with the $\LaTeX$, here is what the data looks like when we plot it:

```{r plot_data, fig.width=5, fig.height=3}
g1 <- ggplot(data=dat, aes(x=x, y=y)) + 
        geom_smooth(method="loess") + 
        geom_point() + 
        theme_classic()
g1
```

## Adding $\LaTeX$

Now for the fun part! You use $\LaTeX$ with the same notation you would in a .tex file, but you need to escape backslashes (for example instead of \\textbf{Hi}, you need to use  \\\\textbf{Hi}).

```{r latex_code}

# here we open a tex file for output, and set the plots dimensions
tikzDevice::tikz(file = "./example_plot.tex", width = 5, height = 3)

# here we add a LaTeX title to the plot
g2 <- g1 + ggtitle("$f(x, \\alpha, \\beta, \\gamma)$")
g2
# closing the graphics device saves the file we opened with tikzDevice::tikz
dev.off()
```

Okay, let's have a look at what the g2 object looks like in R:

```{r examine_g2, fig.width=5, fig.height=3}
print(g2)
```

You can see the $\LaTeX$ code in the title, but not the generated output you would hope to see. However, that output is saved in "*./example_plot.tex*", which you can now include in any .tex document: 

```{r, engine='tikz', fig.ext = 'svg', echo=FALSE, fig.width=5, fig.height=3}
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 29.87, 29.59) rectangle (355.85,193.12);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 29.87, 29.59) rectangle (355.85,193.12);
\definecolor{fillColor}{RGB}{153,153,153}

\path[fill=fillColor,fill opacity=0.40] ( 44.69, 82.86) --
	( 48.44, 79.80) --
	( 52.19, 76.93) --
	( 55.94, 74.26) --
	( 59.69, 71.80) --
	( 63.44, 69.54) --
	( 67.19, 67.50) --
	( 70.94, 65.68) --
	( 74.70, 64.07) --
	( 78.45, 62.68) --
	( 82.20, 61.50) --
	( 85.95, 60.53) --
	( 89.70, 59.75) --
	( 93.45, 59.15) --
	( 97.20, 58.73) --
	(100.95, 58.48) --
	(104.71, 58.31) --
	(108.46, 58.07) --
	(112.21, 57.82) --
	(115.96, 57.61) --
	(119.71, 57.52) --
	(123.46, 57.59) --
	(127.21, 57.90) --
	(130.96, 58.50) --
	(134.72, 59.44) --
	(138.47, 60.51) --
	(142.22, 61.52) --
	(145.97, 62.86) --
	(149.72, 64.82) --
	(153.47, 67.48) --
	(157.22, 70.66) --
	(160.97, 74.40) --
	(164.73, 78.69) --
	(168.48, 83.41) --
	(172.23, 88.33) --
	(175.98, 94.24) --
	(179.73,101.57) --
	(183.48,109.73) --
	(187.23,118.04) --
	(190.98,125.70) --
	(194.74,131.86) --
	(198.49,137.00) --
	(202.24,142.02) --
	(205.99,146.91) --
	(209.74,151.63) --
	(213.49,156.10) --
	(217.24,160.19) --
	(220.99,163.74) --
	(224.74,166.58) --
	(228.50,168.86) --
	(232.25,170.83) --
	(236.00,172.64) --
	(239.75,174.38) --
	(243.50,176.11) --
	(247.25,177.72) --
	(251.00,179.17) --
	(254.75,180.45) --
	(258.51,181.56) --
	(262.26,182.50) --
	(266.01,183.27) --
	(269.76,183.89) --
	(273.51,184.34) --
	(277.26,184.66) --
	(281.01,184.83) --
	(284.76,184.87) --
	(288.52,184.80) --
	(292.27,184.60) --
	(296.02,184.29) --
	(299.77,183.87) --
	(303.52,183.34) --
	(307.27,182.71) --
	(311.02,181.96) --
	(314.77,181.12) --
	(318.53,180.16) --
	(322.28,179.09) --
	(326.03,177.92) --
	(329.78,176.63) --
	(333.53,175.23) --
	(337.28,173.71) --
	(341.03,172.07) --
	(341.03,124.50) --
	(337.28,129.26) --
	(333.53,133.77) --
	(329.78,138.00) --
	(326.03,141.97) --
	(322.28,145.67) --
	(318.53,149.10) --
	(314.77,152.27) --
	(311.02,155.16) --
	(307.27,157.78) --
	(303.52,160.13) --
	(299.77,162.21) --
	(296.02,164.02) --
	(292.27,165.56) --
	(288.52,166.84) --
	(284.76,167.87) --
	(281.01,168.64) --
	(277.26,169.17) --
	(273.51,169.46) --
	(269.76,169.53) --
	(266.01,169.38) --
	(262.26,169.02) --
	(258.51,168.45) --
	(254.75,167.68) --
	(251.00,166.71) --
	(247.25,165.54) --
	(243.50,164.17) --
	(239.75,162.65) --
	(236.00,161.13) --
	(232.25,159.44) --
	(228.50,157.45) --
	(224.74,155.05) --
	(220.99,152.15) --
	(217.24,148.67) --
	(213.49,144.63) --
	(209.74,140.08) --
	(205.99,135.10) --
	(202.24,129.81) --
	(198.49,124.39) --
	(194.74,119.02) --
	(190.98,112.97) --
	(187.23,105.62) --
	(183.48, 97.55) --
	(179.73, 89.41) --
	(175.98, 81.98) --
	(172.23, 76.08) --
	(168.48, 71.53) --
	(164.73, 67.39) --
	(160.97, 63.56) --
	(157.22, 59.99) --
	(153.47, 56.78) --
	(149.72, 54.12) --
	(145.97, 52.22) --
	(142.22, 50.81) --
	(138.47, 49.59) --
	(134.72, 48.37) --
	(130.96, 47.34) --
	(127.21, 46.64) --
	(123.46, 46.22) --
	(119.71, 46.01) --
	(115.96, 45.96) --
	(112.21, 46.02) --
	(108.46, 46.13) --
	(104.71, 46.25) --
	(100.95, 46.33) --
	( 97.20, 46.47) --
	( 93.45, 46.73) --
	( 89.70, 47.08) --
	( 85.95, 47.52) --
	( 82.20, 48.03) --
	( 78.45, 48.59) --
	( 74.70, 49.18) --
	( 70.94, 49.80) --
	( 67.19, 50.43) --
	( 63.44, 51.08) --
	( 59.69, 51.74) --
	( 55.94, 52.40) --
	( 52.19, 53.06) --
	( 48.44, 53.73) --
	( 44.69, 54.39) --
	cycle;
\definecolor{drawColor}{RGB}{51,102,255}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 44.69, 68.63) --
	( 48.44, 66.76) --
	( 52.19, 64.99) --
	( 55.94, 63.33) --
	( 59.69, 61.77) --
	( 63.44, 60.31) --
	( 67.19, 58.97) --
	( 70.94, 57.74) --
	( 74.70, 56.62) --
	( 78.45, 55.63) --
	( 82.20, 54.77) --
	( 85.95, 54.02) --
	( 89.70, 53.42) --
	( 93.45, 52.94) --
	( 97.20, 52.60) --
	(100.95, 52.41) --
	(104.71, 52.28) --
	(108.46, 52.10) --
	(112.21, 51.92) --
	(115.96, 51.79) --
	(119.71, 51.76) --
	(123.46, 51.91) --
	(127.21, 52.27) --
	(130.96, 52.92) --
	(134.72, 53.90) --
	(138.47, 55.05) --
	(142.22, 56.17) --
	(145.97, 57.54) --
	(149.72, 59.47) --
	(153.47, 62.13) --
	(157.22, 65.33) --
	(160.97, 68.98) --
	(164.73, 73.04) --
	(168.48, 77.47) --
	(172.23, 82.21) --
	(175.98, 88.11) --
	(179.73, 95.49) --
	(183.48,103.64) --
	(187.23,111.83) --
	(190.98,119.33) --
	(194.74,125.44) --
	(198.49,130.69) --
	(202.24,135.91) --
	(205.99,141.00) --
	(209.74,145.85) --
	(213.49,150.36) --
	(217.24,154.43) --
	(220.99,157.95) --
	(224.74,160.82) --
	(228.50,163.16) --
	(232.25,165.14) --
	(236.00,166.88) --
	(239.75,168.52) --
	(243.50,170.14) --
	(247.25,171.63) --
	(251.00,172.94) --
	(254.75,174.07) --
	(258.51,175.00) --
	(262.26,175.76) --
	(266.01,176.33) --
	(269.76,176.71) --
	(273.51,176.90) --
	(277.26,176.91) --
	(281.01,176.74) --
	(284.76,176.37) --
	(288.52,175.82) --
	(292.27,175.08) --
	(296.02,174.15) --
	(299.77,173.04) --
	(303.52,171.73) --
	(307.27,170.24) --
	(311.02,168.56) --
	(314.77,166.69) --
	(318.53,164.63) --
	(322.28,162.38) --
	(326.03,159.94) --
	(329.78,157.32) --
	(333.53,154.50) --
	(337.28,151.49) --
	(341.03,148.29);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.30,121.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (236.35,162.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.11,148.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.76, 40.76) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.29, 57.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.09,165.79) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.28, 71.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.30, 52.64) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (263.09,180.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.14,166.97) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.21,160.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.76, 72.16) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.11, 58.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.76,172.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.12, 73.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.23, 48.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.13, 55.63) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.17, 56.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.10, 78.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.81, 66.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (236.69,174.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.69, 71.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.20,159.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.81, 70.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.77, 60.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.48,172.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.30, 58.00) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.51, 73.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.49,150.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.10, 47.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.37, 74.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.73, 70.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (228.72,146.39) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.97, 48.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.37,141.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.32,148.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.01,116.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.44,160.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.47, 41.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.68, 69.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.35, 63.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (267.80,149.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (318.29,153.60) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.58,169.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (341.03,153.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.40,163.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (234.98,178.79) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.86,154.05) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.94, 59.00) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.02, 50.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.03, 59.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.91, 70.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.24, 55.97) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.43, 87.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.51, 49.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.22,148.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.23, 98.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.61,144.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.15, 95.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.19, 59.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.97, 67.14) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.74, 84.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.22, 45.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.62, 63.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (224.05,142.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.75, 37.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (302.65,185.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.05, 69.22) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (268.97,183.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.49, 73.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.47,162.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.21,160.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.65, 43.88) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.62,140.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.16,171.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.20, 71.60) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (284.01,183.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.11, 52.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.21,159.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.73, 54.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.06,168.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.72,174.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.51,174.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 50.35, 62.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.18,152.03) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.56, 48.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.32, 60.47) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.34, 64.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.86, 61.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.23,100.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.70, 84.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.61, 64.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.84, 60.08) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.56,150.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.94, 51.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.41,157.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.85, 76.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.30,155.76) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.11, 65.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.44, 62.67) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.87, 29.59) --
	( 29.87,193.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92, 59.86) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92,108.83) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92,157.81) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12, 62.89) --
	( 29.87, 62.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12,111.87) --
	( 29.87,111.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12,160.84) --
	( 29.87,160.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.87, 29.59) --
	(355.85, 29.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.13, 26.84) --
	( 67.13, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (127.61, 26.84) --
	(127.61, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.08, 26.84) --
	(188.08, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.56, 26.84) --
	(248.56, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.03, 26.84) --
	(309.03, 29.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 67.13, 18.58) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.61, 18.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (188.08, 18.58) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.56, 18.58) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (309.03, 18.58) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (192.86,  5.50) {x};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,111.35) {y};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 29.87,202.22) {$f(x, \alpha, \beta, \gamma)$};
\end{scope}
\end{tikzpicture}
```

To include this plot in a .tex document, you can use:


    input{example_plot.tex}


But remember to include the **tikz** package!

    \usepackage{tikz}

or (not recommended due to lack of readability) you can copy and paste the contents of the file *example_plot.tex* into your $\LaTeX$ document. If you want to see the contents of the file *example_plot.tex*, scroll down to the **Appendix** (I've put it at the end of this post since the output is a few hundred lines long).

## Title, Labels, Annotations

Here I will show you in one plot how easy it is to add $\LaTeX$ to each of the text components of the plot.


```{r latex_code2, fig.width=5, fig.height=3}
# here we open a tex file for output, and set the plots dimensions
tikzDevice::tikz(file = "./example_plot_2.tex", width = 5, height = 3)

# here we add a some LaTeX to the plot
g3 <- g1 + 
  ggtitle("$f(x, \\alpha, \\beta, \\gamma)$") +
  xlab(label = "$x \\sim rnorm(\\mu=10, \\sigma=10)$") +
  ylab(label = "$f(x)=\\frac{\\alpha}{1 + exp( - \\beta (x-\\gamma) )}+\\varepsilon$") +
  annotate(geom  = "text", 
           x     = c(0,0,0), 
           y     = c(2,1.8,1.6), 
           label = c("$\\alpha=2$", "$\\beta=1.5$", "$\\gamma=10$"),
           hjust = 0)
g3
# closing the graphics device saves the file we opened with tikzDevice::tikz
dev.off()
```


```{r, engine='tikz', fig.ext = 'svg', echo=FALSE, fig.width=5, fig.height=3}
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 30.42, 32.09) rectangle (355.85,193.12);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 30.42, 32.09) rectangle (355.85,193.12);
\definecolor{fillColor}{RGB}{153,153,153}

\path[fill=fillColor,fill opacity=0.40] ( 45.22, 84.54) --
	( 48.96, 81.53) --
	( 52.71, 78.70) --
	( 56.45, 76.08) --
	( 60.20, 73.65) --
	( 63.94, 71.43) --
	( 67.69, 69.42) --
	( 71.43, 67.63) --
	( 75.18, 66.04) --
	( 78.92, 64.67) --
	( 82.66, 63.51) --
	( 86.41, 62.55) --
	( 90.15, 61.78) --
	( 93.90, 61.20) --
	( 97.64, 60.79) --
	(101.39, 60.54) --
	(105.13, 60.37) --
	(108.88, 60.14) --
	(112.62, 59.89) --
	(116.37, 59.68) --
	(120.11, 59.59) --
	(123.86, 59.66) --
	(127.60, 59.97) --
	(131.35, 60.56) --
	(135.09, 61.48) --
	(138.84, 62.53) --
	(142.58, 63.54) --
	(146.33, 64.86) --
	(150.07, 66.78) --
	(153.82, 69.40) --
	(157.56, 72.53) --
	(161.31, 76.21) --
	(165.05, 80.44) --
	(168.80, 85.08) --
	(172.54, 89.94) --
	(176.29, 95.75) --
	(180.03,102.97) --
	(183.78,111.01) --
	(187.52,119.19) --
	(191.26,126.73) --
	(195.01,132.79) --
	(198.75,137.85) --
	(202.50,142.80) --
	(206.24,147.61) --
	(209.99,152.26) --
	(213.73,156.66) --
	(217.48,160.69) --
	(221.22,164.19) --
	(224.97,166.99) --
	(228.71,169.23) --
	(232.46,171.17) --
	(236.20,172.95) --
	(239.95,174.66) --
	(243.69,176.37) --
	(247.44,177.96) --
	(251.18,179.38) --
	(254.93,180.65) --
	(258.67,181.74) --
	(262.42,182.66) --
	(266.16,183.42) --
	(269.91,184.03) --
	(273.65,184.48) --
	(277.40,184.79) --
	(281.14,184.96) --
	(284.89,185.00) --
	(288.63,184.92) --
	(292.38,184.73) --
	(296.12,184.42) --
	(299.86,184.01) --
	(303.61,183.49) --
	(307.35,182.86) --
	(311.10,182.13) --
	(314.84,181.30) --
	(318.59,180.36) --
	(322.33,179.31) --
	(326.08,178.15) --
	(329.82,176.88) --
	(333.57,175.50) --
	(337.31,174.00) --
	(341.06,172.39) --
	(341.06,125.55) --
	(337.31,130.24) --
	(333.57,134.67) --
	(329.82,138.84) --
	(326.08,142.75) --
	(322.33,146.40) --
	(318.59,149.78) --
	(314.84,152.89) --
	(311.10,155.74) --
	(307.35,158.32) --
	(303.61,160.63) --
	(299.86,162.68) --
	(296.12,164.46) --
	(292.38,165.98) --
	(288.63,167.25) --
	(284.89,168.25) --
	(281.14,169.02) --
	(277.40,169.54) --
	(273.65,169.83) --
	(269.91,169.89) --
	(266.16,169.74) --
	(262.42,169.39) --
	(258.67,168.83) --
	(254.93,168.07) --
	(251.18,167.11) --
	(247.44,165.96) --
	(243.69,164.61) --
	(239.95,163.12) --
	(236.20,161.62) --
	(232.46,159.95) --
	(228.71,157.99) --
	(224.97,155.63) --
	(221.22,152.78) --
	(217.48,149.35) --
	(213.73,145.37) --
	(209.99,140.89) --
	(206.24,135.98) --
	(202.50,130.78) --
	(198.75,125.44) --
	(195.01,120.15) --
	(191.26,114.20) --
	(187.52,106.96) --
	(183.78, 99.01) --
	(180.03, 91.00) --
	(176.29, 83.68) --
	(172.54, 77.87) --
	(168.80, 73.39) --
	(165.05, 69.32) --
	(161.31, 65.54) --
	(157.56, 62.02) --
	(153.82, 58.86) --
	(150.07, 56.24) --
	(146.33, 54.37) --
	(142.58, 52.99) --
	(138.84, 51.79) --
	(135.09, 50.58) --
	(131.35, 49.57) --
	(127.60, 48.88) --
	(123.86, 48.47) --
	(120.11, 48.26) --
	(116.37, 48.21) --
	(112.62, 48.27) --
	(108.88, 48.38) --
	(105.13, 48.50) --
	(101.39, 48.57) --
	( 97.64, 48.71) --
	( 93.90, 48.96) --
	( 90.15, 49.32) --
	( 86.41, 49.75) --
	( 82.66, 50.25) --
	( 78.92, 50.79) --
	( 75.18, 51.38) --
	( 71.43, 51.99) --
	( 67.69, 52.61) --
	( 63.94, 53.25) --
	( 60.20, 53.90) --
	( 56.45, 54.55) --
	( 52.71, 55.20) --
	( 48.96, 55.86) --
	( 45.22, 56.51) --
	cycle;
\definecolor{drawColor}{RGB}{51,102,255}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 45.22, 70.53) --
	( 48.96, 68.69) --
	( 52.71, 66.95) --
	( 56.45, 65.31) --
	( 60.20, 63.77) --
	( 63.94, 62.34) --
	( 67.69, 61.02) --
	( 71.43, 59.81) --
	( 75.18, 58.71) --
	( 78.92, 57.73) --
	( 82.66, 56.88) --
	( 86.41, 56.15) --
	( 90.15, 55.55) --
	( 93.90, 55.08) --
	( 97.64, 54.75) --
	(101.39, 54.56) --
	(105.13, 54.43) --
	(108.88, 54.26) --
	(112.62, 54.08) --
	(116.37, 53.95) --
	(120.11, 53.93) --
	(123.86, 54.07) --
	(127.60, 54.43) --
	(131.35, 55.06) --
	(135.09, 56.03) --
	(138.84, 57.16) --
	(142.58, 58.26) --
	(146.33, 59.61) --
	(150.07, 61.51) --
	(153.82, 64.13) --
	(157.56, 67.28) --
	(161.31, 70.88) --
	(165.05, 74.88) --
	(168.80, 79.23) --
	(172.54, 83.90) --
	(176.29, 89.71) --
	(180.03, 96.99) --
	(183.78,105.01) --
	(187.52,113.07) --
	(191.26,120.46) --
	(195.01,126.47) --
	(198.75,131.65) --
	(202.50,136.79) --
	(206.24,141.80) --
	(209.99,146.58) --
	(213.73,151.02) --
	(217.48,155.02) --
	(221.22,158.49) --
	(224.97,161.31) --
	(228.71,163.61) --
	(232.46,165.56) --
	(236.20,167.29) --
	(239.95,168.89) --
	(243.69,170.49) --
	(247.44,171.96) --
	(251.18,173.25) --
	(254.93,174.36) --
	(258.67,175.28) --
	(262.42,176.02) --
	(266.16,176.58) --
	(269.91,176.96) --
	(273.65,177.15) --
	(277.40,177.16) --
	(281.14,176.99) --
	(284.89,176.63) --
	(288.63,176.08) --
	(292.38,175.36) --
	(296.12,174.44) --
	(299.86,173.34) --
	(303.61,172.06) --
	(307.35,170.59) --
	(311.10,168.94) --
	(314.84,167.10) --
	(318.59,165.07) --
	(322.33,162.85) --
	(326.08,160.45) --
	(329.82,157.86) --
	(333.57,155.09) --
	(337.31,152.12) --
	(341.06,148.97);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.59,122.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (236.55,162.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.30,149.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.17, 43.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.70, 59.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.35,166.21) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.70, 73.13) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.60, 54.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (263.25,180.44) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.33,167.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (220.44,161.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.14, 74.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.56, 60.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.94,172.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.51, 75.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.67, 50.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.50, 57.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.52, 58.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47, 80.49) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 65.31, 68.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (236.90,174.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.22, 73.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.43,159.86) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.24, 72.14) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.11, 62.75) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.65,172.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.78, 60.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.84, 75.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.74,151.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.44, 49.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.70, 76.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.03, 72.17) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (228.93,147.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.49, 50.79) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.64,141.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.51,149.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.29,117.51) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.67,160.77) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.83, 43.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.15, 71.54) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.71, 65.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (267.95,150.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (318.35,154.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.76,169.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (341.06,154.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.66,164.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.19,179.01) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.11,154.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 88.39, 61.05) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.38, 52.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.37, 61.92) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.27, 72.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.56, 58.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.74, 88.90) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 52.03, 51.51) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.43,149.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.52,100.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.80,145.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.46, 96.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.54, 61.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.34, 69.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.04, 86.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.60, 47.56) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.99, 65.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (224.28,143.61) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.15, 39.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (302.74,185.80) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.43, 71.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (269.12,184.07) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.82, 75.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (246.66,162.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.47,160.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.00, 46.16) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.89,141.11) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.37,171.79) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.58, 73.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (284.13,183.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.43, 54.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.44,159.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.07, 56.70) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.30,168.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.00,174.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.76,174.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 50.87, 64.68) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.38,152.66) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.96, 50.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.82, 62.50) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.64, 66.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.22, 63.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.51,101.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.18, 85.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.99, 66.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.18, 62.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.82,151.13) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.30, 53.57) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (225.64,158.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.14, 78.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.52,156.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.49, 67.65) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.83, 64.66) circle (  1.96);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (128.00,157.54) {$\alpha=2$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (128.00,147.89) {$\beta=1.5$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (128.00,138.24) {$\gamma=10$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 30.42, 32.09) --
	( 30.42,193.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 25.47, 61.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 25.47,110.08) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 25.47,158.31) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.67, 64.88) --
	( 30.42, 64.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.67,113.11) --
	( 30.42,113.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.67,161.34) --
	( 30.42,161.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 30.42, 32.09) --
	(355.85, 32.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 67.63, 29.34) --
	( 67.63, 32.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (128.00, 29.34) --
	(128.00, 32.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (188.37, 29.34) --
	(188.37, 32.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (248.74, 29.34) --
	(248.74, 32.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (309.11, 29.34) --
	(309.11, 32.09);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 67.63, 21.08) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (128.00, 21.08) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (188.37, 21.08) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.74, 21.08) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (309.11, 21.08) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (193.14,  8.00) {$x \sim rnorm(\mu=10, \sigma=10)$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,112.60) {$f(x)=\frac{\alpha}{1 + exp( - \beta (x-\gamma) )}+\varepsilon$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (361.35,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 30.42,202.22) {$f(x, \alpha, \beta, \gamma)$};
\end{scope}
\end{tikzpicture}
```

## References

I would like to point you towards the tutorial by Ilyass Tabiai, which is where I first learnt about **tikzDevice**: 
<a href="http://iltabiai.github.io/tips/latex/2015/09/15/latex-tikzdevice-r.html"> Latex + R + tikzDevice </a>

As well as the very nice comparison of options made by Rob J Hyndman:
<a href="https://robjhyndman.com/hyndsight/latex2exp/"> Mathematical annotations on R plots
 </a>

## Appendix
<details><summary>*example_plot.tex* (click to expand)</summary>
<p>
```{r,engine='tikz', fig.ext = 'svg', eval=FALSE, fig.width=6, fig.height=4}
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 29.87, 29.59) rectangle (428.12,265.39);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 29.87, 29.59) rectangle (428.12,265.39);
\definecolor{fillColor}{RGB}{153,153,153}

\path[fill=fillColor,fill opacity=0.40] ( 47.97,134.91) --
	( 52.55,129.88) --
	( 57.14,125.09) --
	( 61.72,120.54) --
	( 66.30,116.23) --
	( 70.89,112.17) --
	( 75.47,108.37) --
	( 80.05,104.81) --
	( 84.63,101.52) --
	( 89.22, 98.48) --
	( 93.80, 95.70) --
	( 98.38, 93.18) --
	(102.97, 90.93) --
	(107.55, 88.92) --
	(112.13, 87.17) --
	(116.71, 85.66) --
	(121.30, 84.37) --
	(125.88, 83.30) --
	(130.46, 82.44) --
	(135.05, 81.77) --
	(139.63, 81.27) --
	(144.21, 80.95) --
	(148.79, 80.80) --
	(153.38, 80.81) --
	(157.96, 80.99) --
	(162.54, 81.35) --
	(167.13, 81.55) --
	(171.71, 81.36) --
	(176.29, 81.13) --
	(180.87, 81.19) --
	(185.46, 81.84) --
	(190.04, 83.31) --
	(194.62, 84.61) --
	(199.21, 85.53) --
	(203.79, 87.29) --
	(208.37, 90.85) --
	(212.95, 96.67) --
	(217.54,104.51) --
	(222.12,114.01) --
	(226.70,124.67) --
	(231.29,135.81) --
	(235.87,146.58) --
	(240.45,158.27) --
	(245.03,172.27) --
	(249.62,186.89) --
	(254.20,200.14) --
	(258.78,209.94) --
	(263.37,218.58) --
	(267.95,226.97) --
	(272.53,234.13) --
	(277.11,239.38) --
	(281.70,243.68) --
	(286.28,247.20) --
	(290.86,250.00) --
	(295.45,252.09) --
	(300.03,253.46) --
	(304.61,254.12) --
	(309.19,254.26) --
	(313.78,254.21) --
	(318.36,253.97) --
	(322.94,253.53) --
	(327.53,252.90) --
	(332.11,252.07) --
	(336.69,251.06) --
	(341.27,249.88) --
	(345.86,248.55) --
	(350.44,247.08) --
	(355.02,245.48) --
	(359.61,243.76) --
	(364.19,241.93) --
	(368.77,239.98) --
	(373.35,237.92) --
	(377.94,235.73) --
	(382.52,233.43) --
	(387.10,230.99) --
	(391.69,228.41) --
	(396.27,225.69) --
	(400.85,222.82) --
	(405.43,219.80) --
	(410.02,216.61) --
	(410.02,145.67) --
	(405.43,154.33) --
	(400.85,162.53) --
	(396.27,170.27) --
	(391.69,177.56) --
	(387.10,184.39) --
	(382.52,190.78) --
	(377.94,196.71) --
	(373.35,202.20) --
	(368.77,207.24) --
	(364.19,211.84) --
	(359.61,216.00) --
	(355.02,219.74) --
	(350.44,223.07) --
	(345.86,226.00) --
	(341.27,228.56) --
	(336.69,230.76) --
	(332.11,232.62) --
	(327.53,234.18) --
	(322.94,235.44) --
	(318.36,236.43) --
	(313.78,237.14) --
	(309.19,237.59) --
	(304.61,237.76) --
	(300.03,237.43) --
	(295.45,236.46) --
	(290.86,234.77) --
	(286.28,232.27) --
	(281.70,228.92) --
	(277.11,224.70) --
	(272.53,219.53) --
	(267.95,212.53) --
	(263.37,204.05) --
	(258.78,195.05) --
	(254.20,185.16) --
	(249.62,171.91) --
	(245.03,156.89) --
	(240.45,142.15) --
	(235.87,130.01) --
	(231.29,119.51) --
	(226.70,108.95) --
	(222.12, 98.66) --
	(217.54, 89.14) --
	(212.95, 81.05) --
	(208.37, 75.20) --
	(203.79, 72.06) --
	(199.21, 70.59) --
	(194.62, 69.58) --
	(190.04, 68.12) --
	(185.46, 66.68) --
	(180.87, 66.01) --
	(176.29, 65.77) --
	(171.71, 65.69) --
	(167.13, 65.50) --
	(162.54, 64.98) --
	(157.96, 64.35) --
	(153.38, 63.85) --
	(148.79, 63.49) --
	(144.21, 63.27) --
	(139.63, 63.17) --
	(135.05, 63.19) --
	(130.46, 63.32) --
	(125.88, 63.54) --
	(121.30, 63.82) --
	(116.71, 64.17) --
	(112.13, 64.55) --
	(107.55, 64.96) --
	(102.97, 65.37) --
	( 98.38, 65.78) --
	( 93.80, 66.18) --
	( 89.22, 66.57) --
	( 84.63, 66.93) --
	( 80.05, 67.27) --
	( 75.47, 67.58) --
	( 70.89, 67.87) --
	( 66.30, 68.12) --
	( 61.72, 68.34) --
	( 57.14, 68.53) --
	( 52.55, 68.68) --
	( 47.97, 68.80) --
	cycle;
\definecolor{drawColor}{RGB}{51,102,255}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 47.97,101.85) --
	( 52.55, 99.28) --
	( 57.14, 96.81) --
	( 61.72, 94.44) --
	( 66.30, 92.18) --
	( 70.89, 90.02) --
	( 75.47, 87.97) --
	( 80.05, 86.04) --
	( 84.63, 84.22) --
	( 89.22, 82.52) --
	( 93.80, 80.94) --
	( 98.38, 79.48) --
	(102.97, 78.15) --
	(107.55, 76.94) --
	(112.13, 75.86) --
	(116.71, 74.91) --
	(121.30, 74.10) --
	(125.88, 73.42) --
	(130.46, 72.88) --
	(135.05, 72.48) --
	(139.63, 72.22) --
	(144.21, 72.11) --
	(148.79, 72.15) --
	(153.38, 72.33) --
	(157.96, 72.67) --
	(162.54, 73.16) --
	(167.13, 73.53) --
	(171.71, 73.53) --
	(176.29, 73.45) --
	(180.87, 73.60) --
	(185.46, 74.26) --
	(190.04, 75.72) --
	(194.62, 77.10) --
	(199.21, 78.06) --
	(203.79, 79.68) --
	(208.37, 83.03) --
	(212.95, 88.86) --
	(217.54, 96.83) --
	(222.12,106.34) --
	(226.70,116.81) --
	(231.29,127.66) --
	(235.87,138.30) --
	(240.45,150.21) --
	(245.03,164.58) --
	(249.62,179.40) --
	(254.20,192.65) --
	(258.78,202.50) --
	(263.37,211.31) --
	(267.95,219.75) --
	(272.53,226.83) --
	(277.11,232.04) --
	(281.70,236.30) --
	(286.28,239.74) --
	(290.86,242.38) --
	(295.45,244.28) --
	(300.03,245.45) --
	(304.61,245.94) --
	(309.19,245.92) --
	(313.78,245.67) --
	(318.36,245.20) --
	(322.94,244.49) --
	(327.53,243.54) --
	(332.11,242.34) --
	(336.69,240.91) --
	(341.27,239.22) --
	(345.86,237.28) --
	(350.44,235.08) --
	(355.02,232.61) --
	(359.61,229.88) --
	(364.19,226.88) --
	(368.77,223.61) --
	(373.35,220.06) --
	(377.94,216.22) --
	(382.52,212.10) --
	(387.10,207.69) --
	(391.69,202.99) --
	(396.27,197.98) --
	(400.85,192.68) --
	(405.43,187.06) --
	(410.02,181.14);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (277.94,249.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (233.16, 97.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.90, 64.76) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (251.40,215.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.07, 79.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (327.22,223.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.34, 92.38) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.13, 81.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.54,108.00) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (243.67,169.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.53, 77.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (267.25,231.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.29, 52.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (288.56,244.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (317.32,229.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (257.67,216.96) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.67, 73.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.09,215.04) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.05, 89.41) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.97, 88.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.03,112.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.51, 62.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (308.05,242.51) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.11,254.67) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (328.88,208.82) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.90,197.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.95,223.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.08,146.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (263.92,242.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (248.28,219.28) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.57, 99.90) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (239.13,132.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (329.50,226.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (236.17,115.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.70, 92.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.67, 88.59) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.92, 75.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.62, 90.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.33, 48.06) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.42, 90.40) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (284.67,228.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (410.02,206.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.54, 52.02) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (261.34,205.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.46,113.25) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.03, 71.10) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.51,217.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.38, 90.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.78,116.69) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (268.67,238.48) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.49, 76.90) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.95, 96.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.90,232.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (336.01,222.63) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.14, 93.85) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (228.57, 86.30) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.34,235.46) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.52, 87.24) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (274.04,243.74) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (335.81,212.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (248.99,209.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (233.59,131.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.27, 97.93) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (232.35,108.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (238.08,133.50) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (271.17,215.44) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.39, 56.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.00, 94.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.33, 75.67) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.99,224.62) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.45, 64.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (265.33,247.98) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.30,115.19) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.66, 74.37) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (269.04,215.73) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.86, 75.09) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.96, 80.89) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.79,233.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (289.54,225.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (265.30,237.20) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.56,199.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (285.82,247.51) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.52, 63.83) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (276.44,238.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.32,239.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.93, 40.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.76,115.35) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.51, 83.55) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (309.08,222.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (277.29,211.95) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.44, 89.58) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.84, 95.53) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (252.76,193.64) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (273.30,224.34) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.66, 90.72) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.31, 59.67) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.52, 99.71) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (295.43,226.67) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (237.68,128.12) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (257.73,237.81) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.87, 29.59) --
	( 29.87,265.39);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92, 82.91) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92,153.84) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 24.92,224.77) {2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12, 85.94) --
	( 29.87, 85.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12,156.87) --
	( 29.87,156.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 27.12,227.80) --
	( 29.87,227.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 29.87, 29.59) --
	(428.12, 29.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 46.02, 26.84) --
	( 46.02, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (176.34, 26.84) --
	(176.34, 29.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (306.65, 26.84) --
	(306.65, 29.59);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 46.02, 18.58) {-20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (176.34, 18.58) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (306.65, 18.58) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (228.99,  5.50) {x};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,147.49) {y};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at ( 29.87,274.49) {$f(x, \alpha, \beta, \gamma)$};
\end{scope}
\end{tikzpicture}
```

</p>
</details>




